---
title: "Final Project (Group 2)"
author: "Group 2"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: yes
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
  word_document:
    toc: no
geometry: margin=1in
fontsize: 11pt
documentclass: article
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
is_pdf <- try (("pdf_document" %in% 
                  rmarkdown::all_output_formats(knitr::current_input())), 
               silent=TRUE)
is_pdf <- (is_pdf == TRUE)

# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(infer))
suppressPackageStartupMessages(library(lubridate))
suppressPackageStartupMessages(library(geosphere))
suppressPackageStartupMessages(library(lubridate))
suppressPackageStartupMessages(library(infer))
suppressPackageStartupMessages(library(usmap))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(formattable))
suppressPackageStartupMessages(library(plotrix))
suppressPackageStartupMessages(library(ggpubr))
suppressPackageStartupMessages(library(boot))
suppressPackageStartupMessages(library(infer))
# Load Cohen's d bootstrap helper functions
load("bootstrap_cohens_d.RData")
```

<<<<<<< HEAD
-   Research Question/Hypothesis: What variable in the world happiness report (family, health, trust, generosity, and economics) has the greatest effect on a nation's happiness score?
=======

* Research Question/Hypothesis: 
What variable in the world happiness report (family, health, trust, generosity, and economics) has the greatest effect on a nation’s happiness score? 
>>>>>>> 81e6af9ac23978bbafb85c9fa12c41d73c572ee5

-   Hypothesis: Economics plays the largest role in a nation's happiness score.

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)

data <- read_excel("2019.xls")

colnames(data)

```

```{r}
library(readxl)

data <- read_excel("2019.xls")

print(colnames(data))

data <- data %>%
  rename(
    Economy = `GDP per capita`,  
    Social = 'Social support',                      
    Health = `Healthy life expectancy`,
    Freedom = `Freedom to make life choices`,  
    Corruption = 'Perceptions of corruption', 
    Happiness_Score = `Score`
  )
print(colnames(data))

```

```{r}
  head(
    select(data, Economy, Social, Health, Freedom, Corruption, Happiness_Score)
  )
```

[Module 2: Junhyung Kim, Jiho Lee]

\*Scatter Plot

```{r}
qplot(x = Economy, y= Happiness_Score, data = data,
 geom = c("point", "smooth"), method = "lm") +
 labs(title =
 "Scatter Plot of Relationship Between
 Economy and Happiness Score",
 x = "Economy", y = "Happiness Score")
```

```{r}
 qplot(x= Social,y=Happiness_Score,data=data,
 geom=c("point","smooth"),method="lm")+
 labs(title =
 "Scatter Plot of Relationship Between
 Social and Happiness Score",
 x="Social",y="Happiness Score")
```

```{r}
qplot(x= Health,y=Happiness_Score,data=data,
 geom=c("point","smooth"),method="lm")+
 labs(title =
 "Scatter Plot of Relationship Between
 Health and Happiness Score",
 x="Health",y="Happiness Score")
```

```{r, warning = FALSE}
qplot(x= Freedom,y=Happiness_Score,data=data,
 geom=c("point","smooth"),method="lm")+
 labs(title =
 "Scatter Plot of Relationship Between
 Freedom and Happiness Score",
 x="Freedom",y="Happiness Score")
```

```{r, warning = FALSE}
 qplot(x= Corruption,y=Happiness_Score,data=data,
 geom=c("point","smooth"),method="lm")+
 labs(title ="Scatter Plot of Relationship Between
 Corruption and Happiness Score",
 x="Corruption",y="HappinessScore")
```

```{r}
data %>%
  ggplot() +
  geom_smooth(mapping = aes(x = Economy, y = Happiness_Score)) +
  labs(x = "Economy", y = "Happiness Score", 
       title="Trend line relationship between 
       Economy vs Happiness Score")
```

```{r}
data %>%
  ggplot() +
  geom_smooth(mapping = aes(x = Social, y = Happiness_Score)) +
  labs(x = "Social", y = "Happiness Score", 
       title="Trend line relationship between 
       Social vs Happiness Score")
```

```{r}
data %>%
  ggplot() +
  geom_smooth(mapping = aes(x = Health, y = Happiness_Score)) +
  labs(x = "Health", y = "Happiness Score", 
       title="Trend line relationship between 
       Health vs Happiness Score")
```

```{r}
data %>%
  ggplot() +
  geom_smooth(mapping = aes(x = Freedom, y = Happiness_Score)) +
  labs(x = "Freedom", y = "Happiness Score", 
       title="Trend line relationship between 
       Freedom vs Happiness Score")
```

```{r}
data %>%
  ggplot() +
  geom_smooth(mapping = aes(x = Corruption, y = Happiness_Score)) +
  labs(x = "Corruption", y = "Happiness Score", 
       title="Trend line relationship between 
       Corruption vs Happiness Score")
```

\*HeatMap

```{r}
data %>%
ggplot(aes(x = Economy, y = Happiness_Score)) +
  geom_bin2d(bins = 30) +  
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "HeatMap with linearline 
                Economy vs Happiness Score", 
           x = "Economy", y = "Happiness_Score")
```


```{r}
data %>%
ggplot(aes(x = Social, y = Happiness_Score)) +
  geom_bin2d(bins = 30) +  
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "HeatMap with linearline 
                Social vs Happiness Score", 
           x = "Social", y = "Happiness_Score")
```


```{r}
data %>%
ggplot(aes(x = Health, y = Happiness_Score)) +
  geom_bin2d(bins = 30) +  
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "HeatMap with linearline 
                Health vs Happiness Score", 
           x = "Health", y = "Happiness_Score")
```


```{r}
data %>%
ggplot(aes(x = Freedom, y = Happiness_Score)) +
  geom_bin2d(bins = 30) +  
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "HeatMap with linearline 
                Freedom and Happiness Score", 
           x = "Freedom", y = "Happiness_Score")
```


```{r}
data %>%
ggplot(aes(x = Corruption, y = Happiness_Score)) +
  geom_bin2d(bins = 30) +  
  geom_smooth(method = "lm", se = FALSE) + 
  labs(title = "HeatMap with linearline
                Corruption and Happiness Score", 
           x = "Corruption", y = "Happiness_Score")
```


======= [ Module 4: Eugene Kim, Harold Lee - Explanatory Data Analysis ]


```{r}
str(data, vec.len = 2)
head(
    select(data, Economy, Social, Health, Freedom, Corruption,
           Happiness_Score)
  )
tail(select(data, Economy, Social, Health, Freedom, Corruption,
            Happiness_Score)
  )
```

\*Summary statistics

\*Box Plot

```{r}
data_long <- data %>%
  gather(key = "Variable", value = "Score", Economy, Social, Health,
         Freedom, Corruption) 

ggplot(data_long, aes(x = Variable, y = Score)) +
  geom_boxplot(width = 0.7) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Box Plot Each Variable",
       x = "Variables Affecting Happiness Score", y = "Values")
```

\*Violin Plot

```{r}
ggplot(data_long, aes(x = Variable, y = Score, fill = Variable)) +
  geom_violin(trim = TRUE) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Violin Plot of Each Variable",
       x = "Variables Affecting Happiness Score", y = "Values") +
  scale_fill_brewer(palette = "Pastel1")
```

\*Summary

```{r}
data %>%
  summarize(
    mean= mean(Economy),
    median = median(Economy),
    sd = sd(Economy),
    iqr = IQR(Economy),
    min = min(Economy),
    max = max(Economy)
 )
```

```{r}
data %>%
  summarize(
    mean= mean(Social),
    median = median(Social),
    sd = sd(Social),
    iqr = IQR(Social),
    min = min(Social),
    max = max(Social)
 )
```

```{r}
data %>%
  summarize(
    mean= mean(Health),
    median = median(Health),
    sd = sd(Health),
    iqr = IQR(Health),
    min = min(Health),
    max = max(Health)
 )
```

```{r}
data %>%
  summarize(
    mean= mean(Freedom),
    median = median(Freedom),
    sd = sd(Freedom),
    iqr = IQR(Freedom),
    min = min(Freedom),
    max = max(Freedom)
 )
```

```{r}
data %>%
  summarize(
    mean= mean(Corruption),
    median = median(Corruption),
    sd = sd(Corruption),
    iqr = IQR(Corruption),
    min = min(Corruption),
    max = max(Corruption)
 )
```



```{r}
data_E <- data %>%
  summarize(
    mean= mean(Economy),
    median = median(Economy),
    sd = sd(Economy),
    iqr = IQR(Economy),
    min = min(Economy),
    max = max(Economy)
 )
```

```{r}
data_S <- data %>%
  summarize(
    mean= mean(Social),
    median = median(Social),
    sd = sd(Social),
    iqr = IQR(Social),
    min = min(Social),
    max = max(Social)
 )
```

```{r}
data_H <- data %>%
  summarize(
    mean= mean(Health),
    median = median(Health),
    sd = sd(Health),
    iqr = IQR(Health),
    min = min(Health),
    max = max(Health)
 )
```

```{r}
data_F <- data %>%
  summarize(
    mean= mean(Freedom),
    median = median(Freedom),
    sd = sd(Freedom),
    iqr = IQR(Freedom),
    min = min(Freedom),
    max = max(Freedom)
 )
```

```{r}
data_C <- data %>%
  summarize(
    mean= mean(Corruption),
    median = median(Corruption),
    sd = sd(Corruption),
    iqr = IQR(Corruption),
    min = min(Corruption),
    max = max(Corruption)
 )
```

```{r}
combined_data <- rbind(data_E, data_S, data_H, data_F, data_C)
```

```{r}
combined_data_rounded <- combined_data %>%
  mutate(across(everything(), ~ round(., 2)))
```

```{r}
row.names(combined_data_rounded) <- c("Economy", "Social", "Health","Freedom", "Corruption")
print(combined_data_rounded)
```

# [Module 5: Chun Jin Park - Modeling]

# Linear model using Im

```{r}
model <- lm(Happiness_Score ~ Economy + Social + Health + Freedom + Generosity
            + Corruption, data = data)

summary(model)
```

# Tidy to get the model coefficients

```{r}
coefficients <- tidy(model)
print(coefficients)
```

# Glance to get the model's performance metrics

```{r}
performance <- glance(model)
print(performance)
```

# Observed vs Predicted plot

```{r}
ggplot(data, aes(x = predict(model), y = Happiness_Score)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, col = "red") +
  labs(title = 
         "Observed vs Predicted Happiness Score", 
       x = "Predicted Happiness Score", 
       y = "Observed Happiness Score")
```

# Residuals vs Predicted plot

```{r}
ggplot(data, aes(x = predict(model), y = residuals(model))) +
  geom_point() +
  geom_hline(yintercept = 0, col = "red") +
  labs(title = "Residuals vs Predicted Happiness Score",
       x = "Predicted Happiness Score", 
       y = "Residuals")
```

# Q-Q plot

```{r}
qqnorm(residuals(model))
qqline(residuals(model), col = "red")
```

[Module 6: Sena Julsdorf and Hyeongseok Sim]

```{r}
ggplot(data, aes(x = Economy, y = Happiness_Score)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, col = "blue") +
  labs(title = "Scatter Plot of Happiness Score based on Economy", 
       x = "Economic Score", 
       y = "Happiness Score")
```

```{r}
library(ggplot2)
library(caTools)
```

```{r}
set.seed(123)
split <- sample.split(data$Happiness_Score, SplitRatio = 0.5)
training_set <- subset(data, split == TRUE)
testing_set <- subset(data, split == FALSE)
```

```{r}
lmmodel <- lm(Happiness_Score ~ Economy, data = testing_set)
summary(lmmodel)
```

```{r}
predictions <- predict(lmmodel, newdata = testing_set)
```

```{r}
rmse <- sqrt(mean((testing_set$Happiness_Score - predictions)^2))
print(paste("RMSE: ", rmse))
```
```{r}
r_squared <- summary(lmmodel)$r.squared
print(paste("R-squared: ", r_squared))
```

```{r}
ggplot(data, aes(x = Social, y = Happiness_Score)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, col = "blue") +
  labs(title = "Scatter Plot of Happiness Score based on Social", 
       x = "Social Score", 
       y = "Happiness Score")
```

```{r}
lmmodel_2 <- lm(Happiness_Score ~ Social, data = testing_set)
summary(lmmodel_2)
```
```{r}
predictions_2 <- predict(lmmodel_2, newdata = testing_set)
```

```{r}
rmse_2 <- sqrt(mean((testing_set$Happiness_Score - predictions_2)^2))
print(paste("RMSE (Social model): ", rmse_2))
```

```{r}
r_squared_2 <- summary(lmmodel_2)$r.squared
print(paste("R-squared (Social model): ", r_squared_2))
```

```{r}
ggplot(data, aes(x = Freedom, y = Happiness_Score)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, col = "blue") +
  labs(title = "Scatter Plot of Happiness Score based on Freedom", 
       x = "Freedom Score", 
       y = "Happiness Score")
```

```{r}
lmmodel_3 <- lm(Happiness_Score ~ Freedom, data = testing_set)
summary(lmmodel_3)
```

```{r}
predictions_3 <- predict(lmmodel_3, newdata = testing_set)
```

```{r}
rmse_3 <- sqrt(mean((testing_set$Happiness_Score - predictions_3)^2))
print(paste("RMSE (Freedom model): ", rmse_3))
```

```{r}
r_squared_3 <- summary(lmmodel_3)$r.squared
print(paste("R-squared (Freedom model): ", r_squared_3))
```

```{r}
ggplot(data, aes(x = Health, y = Happiness_Score)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, col = "blue") +
  labs(title = "Scatter Plot of Happiness Score based on Health", 
       x = "Health Score", 
       y = "Happiness Score")
```

```{r}
lmmodel_4 <- lm(Happiness_Score ~ Health, data = testing_set)
summary(lmmodel_4)
```
```{r}
predictions_4 <- predict(lmmodel_4, newdata = testing_set)
```

```{r}
rmse_4 <- sqrt(mean((testing_set$Happiness_Score - predictions_4)^2))
print(paste("RMSE (Health model): ", rmse_4))
```

```{r}
r_squared_4 <- summary(lmmodel_4)$r.squared
print(paste("R-squared (Health model): ", r_squared_4))
```

```{r}
lmmodel_5 <- lm(Happiness_Score ~ Economy, data = training_set)
summary(lmmodel_5)
```

```{r}
predictions_5 <- predict(lmmodel, newdata = training_set)
```

```{r}
rmse_5 <- sqrt(mean((testing_set$Happiness_Score - predictions_5)^2))
print(paste("RMSE: ", rmse))
```

```{r}
r_squared_5 <- summary(lmmodel_5)$r.squared
```

```{r}
print(paste("R-squared (Economy model): ", r_squared_5))
```


